---
title: "Number and Timing of Ambulatory Blood Pressure Monitoring Measurements"
bibliography: refs.bib
csl: aje.csl
output: 
  officedown::rdocx_document:
    reference_docx: aje.docx
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)

library(officedown)
library(officer)
library(flextable)
library(dplyr)

drake::loadd(report_tables)

tbls <- report_tables$tables %>% 
  mutate(caption = paste(pre_cap, caption, sep = ': '))

inline <- report_tables$inline


```

Byron C. Jaeger, PhD^a^, Oluwasegun P. Akinyelure, MD^b^, Swati Sakhuja, MPH^b^, Joshua D. Bundy, PhD, MPH^c^, Cora E. Lewis, MD MSPH^b^, Yuichiro Yano, MD, PhD^d^, George Howard, DrPH^a^, Daichi Shimbo, MD^e^, Paul Muntner, PhD^b^, Joseph E. Schwartz, PhD^e,f^

a.	Department of Biostatistics, University of Alabama at Birmingham, Birmingham, AL

b.	Department of Epidemiology, University of Alabama at Birmingham, Birmingham, AL

c.	Department of Epidemiology, Tulane University School of Public Health and Tropical Medicine, New Orleans, LA

d.	Department of Medicine, Duke University, Durham, NC

e.	Department of Medicine, Columbia University Irving Medical Center, New York City, NY

f.	Department of Psychiatry, Stony Brook School of Medicine, Stony Brook, NY

<br>

__Word count exclusive of references, tables, and figure legends__

- Abstract:

- Text: 

<br>

__Conflict of Interest__

PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript. All other authors have nothing to disclose.

\newpage

# ABSTRACT

Ambulatory blood pressure (BP) monitoring (ABPM) may cause sleep disturbances. Some home BP monitoring (HBPM) devices are able to obtain a limited number of readings at specific times during sleep. Determining whether a small number of BP measurements taken at specific times could reliably assess sleep BP could inform the use of these devices. We used data from the Jackson Heart Study (JHS; N=`r inline$exclusions$exc_4_all_bps$JHS`) and the Coronary Artery Risk Development in Young Adults (CARDIA; N=`r inline$exclusions$exc_4_all_bps$CARDIA`) study to evaluate 74 approaches to sample BP measurements during sleep. We sampled 2 to 4 BP measurements from a full ABPM assessment (i.e., all ABPM measurements during sleep) obtained at specific clock times and times relative to the start of sleep. Sampling BP at 1, 2, 4, and 5 hours after falling asleep provided the highest agreement with full a ABPM in classification of nocturnal hypertension: Kappa statistic (95% CI) `r inline$accuracy$bp_4_Distributed$at_1_2_4_and_5_hours_after_sleep$tbv_kap_Overall`. There was no evidence of a difference in C-statistics for left-ventricular hypertrophy or albuminuria when BP was sampled at 1, 2, 4, and 5 hours after falling asleep compared to sampling BP throughout sleep (p = 0.67). Using four BP measurements at 1, 2, 4, and 5 hours after falling asleep provides high agreement with a full ABPM assessment.

\newpage

Higher blood pressure (BP) levels during sleep have been associated with an increased risk for cardiovascular disease (CVD) and target organ damage, independent of BP measured in a clinical setting [@obrien_european_2013; @parati_european_2014; @shimamoto_japanese_2014; @friedman_can_2009; @yano_association_2019; @kario_nocturnal_2018]. Ambulatory BP monitoring (ABPM) typically measures BP every 15 to 30 minutes throughout the day and night [@pickering_ambulatory_2006]. Although most people find ABPM acceptable, it may cause sleep disturbances for some individuals [@ernst_favorable_2003; @degaute_does_1992; @agarwal_effect_2010]. Home BP monitoring (HBPM) is another approach for measuring BP outside of the office setting and some HBPM devices can be programmed to measure BP at specific times, including when someone is asleep. For instance, Kario et. al. and Ishikawa et. al. reported on an HBPM device that is put on before going to sleep and measures BP at 2:00, 3:00, and 4:00 AM [@kario2015sleep; @ishikawa2014assessment]. 

<br>

Obtaining fewer BP readings during sleep with HBPM instead of ABPM devices may reduce discomfort and disrupted sleep. However, less frequent measurement of BP using HBPM instead of ABPM may result in a loss of information and a weaker association with outcomes [@kario_home_2014]. Few studies have considered the number and timing of BP measurements required to obtain an estimate of BP during sleep similar to that obtained by a full ABPM recording (i.e., using ABPM throughout sleep). Using data from participants in the Jackson Heart Study (JHS) and the Coronary Artery Risk Development in Young Adults (CARDIA) study who underwent 24‐hour ABPM, we evaluated a total of 74 variations on sampling BP during sleep. Each BP sampling variant selected a subset of 2 to 4 BP measurements from all of the BP measurements taken during sleep.

<br>

# METHODS

## _Study population_

The JHS, a community-based prospective cohort study, was designed to evaluate the etiology of CVD among African Americans [@taylor_jr_toward_2005]. The JHS enrolled 5,306 non-institutionalized African Americans aged ≥ 21 years from the Jackson, MS metropolitan area between 2000 and 2004. At the baseline JHS visit, 1,146 participants elected to undergo ABPM. The CARDIA study was designed to examine the development and determinants of clinical and subclinical CVD and their risk factors [@friedman_cardia]. The CARDIA study recruited 5,115 participants, 18 to 30 years of age, at four field centers in the United States (Birmingham, AL; Chicago, IL; Minneapolis, MN; and Oakland, CA) in 1985-1986. During the Year 30 Exam (2015-2016), 831 CARDIA participants enrolled in an ABPM ancillary study conducted in the Birmingham, AL and Chicago, IL field centers. 

<br>

We included participants who slept ≥ 5 hours during their ABPM assessment and recorded ≥ 1 valid BP measurement every 30 minutes from midnight to 5:00 AM during their ABPM assessment (N = `r inline$exclusions$exc_4_all_bps$JHS` JHS and `r inline$exclusions$exc_4_all_bps$CARDIA` CARDIA participants; Table S1). Conduct of each study was approved by institutional review boards at the participating institutions and the current analysis was approved by the University of Alabama at Birmingham Institutional Review Board. Written informed consent was obtained from all participants. 

<br>

## _Ambulatory blood pressure monitoring_ 

In the JHS, ABPM was conducted using the SpaceLabs model 90207 device (SpaceLabs Healthcare, Snoqualmie, WA), which has been previously validated, and BP was measured every 20 minutes over a 24-hour period [@obrien_accuracy_1991]. JHS participants self-reported the times they went to sleep and woke up while wearing the ABPM device.  In CARDIA, ABPM was conducted using the SpaceLabs OnTrak model 90227 device (SpaceLabs Healthcare, Snoqualmie, WA), which has also been previously validated, with an appropriately sized cuff and BP was measured every 30 minutes over a 24-hour period [@greef_validation_nodate]. CARDIA participants also wore an Actiwatch activity monitor (Philips Respironics, Murrysville, PA) on the wrist of their non-dominant arm. In CARDIA, awake and asleep time periods were determined using the activity monitor data in conjunction with participants’ self-reported awake and asleep times. 

## _Blood pressure sampling strategies and variations_

We considered 'distributed' and 'consecutive' strategies to sample BP during sleep (Figure 1). The distributed strategy sampled BP from the full ABPM assessment with intervals between measurements spanning at least 1 hour. The consecutive strategy sampled BP from the full ABPM assessment in consecutive measurements of BP. We considered 25 distributed and 12 consecutive BP sampling variations, and implemented each variation using hours since midnight and hours since falling asleep to identify sampling times. In total, we evaluated 74 different variations on sampling BP: (25 distributed variations + 12 consecutive variations) * 2 time definitions = 74 variations in total. 

## _Nocturnal hypertension_

For JHS and CARDIA participants, nocturnal hypertension according to ABPM was defined by a mean SBP ≥ 120 mm Hg or mean DBP ≥ 70 mm Hg based on all valid BP measurements during sleep. For all BP sampling variations, nocturnal hypertension was defined with the same BP thresholds but using the mean of the 2 to 4 BP measurements that were sampled from the full ABPM assessment.

_Left ventricular hypertrophy and albuminuria_

Echocardiograms and urine specimens were assessed during the Year 30 Exam for CARDIA participants and during the baseline study visit for JHS participants. Left ventricular mass was determined and indexed to body surface area to obtain left ventricular mass index (LMVI) according to recommendations from the American Society of Echocardiography and European Association of Cardiovascular Imaging [@lang_recommendations_2015]. Left ventricular hypertrophy (LVH) was defined as LVMI > 95 g/m^2^ in women and > 115 g/m^2^ in men. Urine specimens were used to measure urinary albumin and creatinine excretion, which were used to calculate the urine albumin-to-creatinine ratio (ACR). ACR was quantified using a 24-hour urine sample in the JHS, if available. Otherwise, a spot urine sample was used. In CARDIA, a spot urine sample was collected for all willing participants. Albuminuria was defined as an ACR ≥ 30 mg/g. 

## _Statistical analyses_

```{r}
# R version string with date spelled out in words
R_string <- glue::glue(
  "R version {version$major}.{version$minor} (Vienna, Austria)"
)

```

Participant characteristics were summarized for the overall population and stratified by study cohort. The count and percent of missing values for each study variable were examined. Differences in mean SBP and DBP during sleep, LVH, and albuminuria were compared between study cohorts using t- and chi-square tests for continuous and categorical variables, respectively. Analyses were conducted using base `r R_string` and a number of additional open-source R packages [@r_language; @wickham_welcome_2019; @cite_drake; @buuren_mice_2010; @cite_table.glue].  



# RESULTS

# DISCUSSION

<!-- MAIN TABLES -->
\newpage
<!-- TABLE 1: CHARACTERISTICS -->
`r tbls$caption[1]` 
`r fp_par(line_spacing = 1)`
`r tbls$object[[1]]`
\newpage
<!-- TABLE 2: BP SAMPLER ACCURACY -->
<!---BLOCK_LANDSCAPE_START--->
`r tbls$caption[2]` 
`r fp_par(line_spacing = 1)`
`r tbls$object[[2]]`
<!---BLOCK_LANDSCAPE_STOP--->
\newpage
<!-- MAIN FIGURES  -->
<!-- SUPP TABLES -->
# SUPPLEMENT
\newpage
`r tbls$caption[3]` 
`r fp_par(line_spacing = 1)`
`r tbls$object[[3]]`
\newpage
# REFERENCES